### 2014-09-26 analysis/context_permeability.Rmd
context_permeability Rmd modified

We will start by loading the dependencies for this report.
```{r}
source("../R/read_network.R")
source("../R/experiment_utils.R")

@@

# Convergence for K-Regular Networks #
In this analysis we look at the convergence to consensus for simulations that use 
regular networks only. We will analyse two things: the *percentage of convergence to total consensus* and the *number of encounters* necessary to achieve concensus.

We first load the data related to convergence to consensus. In this first dataset, we can find a single boolean variable {1,0} that tells us wheather or not consensus was achieved. 
```{r results='asis',message=FALSE}

@@

table <- cast(convergence_data, networks~k, value="convergence")
latex_table <- tabular.cast_df(table)
```
We can now create a table to display the percentage of convergences to total 
consensus **for each value of k and number of networks**.

@@

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively. We look at **configurations with a number of networks >= 3** since less networks lead to much worse results. As we have seen in the previous convergence results.
```{r}
plot <- plot.exp.box(data=fedata_net1,x_factor=as.factor(fedata_net1$num.networks), data_y=fedata_net1$value, fill_factor=as.factor(fedata_net1$network.0.k),fill_label="K", x_label="Number of Networks", y_label="Number of Encounters")

>>>>

We will start by loading the dependencies for this analysis.
```{r}
source("../R/read_network.R")
source("../R/experiment_utils.R")

@@

# Convergence for K-Regular Networks #
In this analysis we look at the convergence to consensus for simulations that use 
regular networks only. We will analyse two things: the *rate of convergence to total consensus* and the *number of encounters* necessary to achieve concensus.

We first load the data related to convergence to consensus. In this first dataset, we can find a single boolean variable {1,0} that tells us wheather or not consensus was achieved. Tipically in all our experiments, we perform 100 independent runs, since we felt 100 runs were not enough to give us an accurate convergence ratio, we run an additional experiment in this case, were each configuration was tested in 3000 independent simulation runs.
```{r results='asis',message=FALSE}

@@

table <- cast(convergence_data, networks~k, value="convergence")
latex_table <- tabular.cast_df(table)
```
We can now create a table to display the percentage of convergences to total 
consensus **for each value of k and number of networks**. We use the aggregate function to compute the convergence ratio.

@@

Now to observe the distribution of the number of encounters, necessary to achieve consensus, we look at the box plots for **k = {1,2,3,4,5}** and **k = {10,20,30,40,50}** respectively. We look at **configurations with a number of networks >= 3** since less networks lead to much worse results. As we have seen in the previous convergence results. We use the ggplot2 library to create the box plots in this case. (you can check the source at ../R/experiment_utils.R)
```{r}
plot <- plot.exp.box(data=fedata_net1,x_factor=as.factor(fedata_net1$num.networks), data_y=fedata_net1$value, fill_factor=as.factor(fedata_net1$network.0.k),fill_label="K", x_label="Number of Networks", y_label="Number of Encounters")
